
---
title: "groupwork2"
output:  
  pdf_document:
          number_sections: yes
fig_caption: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r pacakages}
library(ggplot2)
library(qcc)
library(arm)
library(jtools)
library(ggstatsplot)
library(pscl)
library(lmtest)
library(ggpubr)
library(broom)
library(ggstance)
library(MASS)
```

## 1.Description of the problem

(Describe the data set, the problem, the methods used.)
dfgdfg
```{r loading data}
data12 <-read.csv("dataset12.csv")
data12<-na.omit(data12)

```

## 2.Exploratory data analysis

2.1  Descriptive statistics for independent variables

```{r boxplot for Independent variables}
unique(data12$animal_type)
p1 <- ggplot(data=data12,aes(x=animal_type,y=time_at_shelter))
p1+geom_boxplot()
p1+geom_boxplot(aes(fill=animal_type))
```
Box plot for animal_type.

```
unique(data12$intake_type)
p2 <- ggplot(data=data12,aes(x=intake_type,y=time_at_shelter))
p2+geom_boxplot()
p2+geom_boxplot(aes(fill=intake_type))
```
Box plot for intake_type.
```
unique(data12$outcome_type)
p3 <- ggplot(data=data12,aes(x=outcome_type,y=time_at_shelter))
p3+geom_boxplot()
p3+geom_boxplot(aes(fill=outcome_type))
```
Box plot for outcome_type.

```
unique(data12$chip_status)
p4 <- ggplot(data=data12,aes(x=chip_status,y=time_at_shelter))
p4+geom_boxplot()
p4+geom_boxplot(aes(fill=chip_status))
```
Box plot for chip_status.

```
unique(data12$year)
data12$year <- as.character(data12$year)
p5 <- ggplot(data=data12,aes(x=year,y=time_at_shelter))
p5+geom_boxplot()
p5+geom_boxplot(aes(fill=year))
```
Box plot for year.

(Box line diagram description)

2.2 Determining the distribution of response variables

```{r}
summary(data12$time_at_shelter)

ggplot(data=data12,aes(x=time_at_shelter))+
  geom_histogram(aes(y=..density..),colour="black", fill="white",breaks=seq(0,80,6))+
  xlim(0,80)+
  geom_density(alpha=.2, fill="red")
```



## 3.Building a glm Poisson regression model

(Explain the glm model, the Poisson family of distributions, and why we chose the Poisson distribution for the glm regression.)


```{r poison model}
fitglm <- glm(time_at_shelter ~ animal_type + intake_type + outcome_type + chip_status,
                data = data12,family = poisson)
summary(fitglm)
```
Exponentiated to better explain the model parameters.

The problem of excessive departure from the potential needs attention in #Poisson regression. The mean and variance are equal in a Poisson distribution.
Such a problem may arise in Poisson regression when the actual distribution of the observed response variable does not satisfy this.

## 4.Model testing and Model Correction

The general cause of this problem is the lack of explanatory variables. We can use the qcc package for Poisson models to test for overdiscrepancy.
```{r}
qcc.overdispersion.test(data12$time_at_shelter, type = "poisson")
```
p-values are 0, there is an excessive departure from the potential and a Poisson-like model is chosen for modelling

Next, test the mean and variance
```{r}
mean(data12$time_at_shelter)
var(data12$time_at_shelter)
```
By examining the mean and variance, it was found that the variance was much larger than the mean, indicating that there would be overdispersion in the model

## 5.Model Correction

5.1 Poisson-like distribution models

```{r quasipoisson model}

fitquasi <- glm(time_at_shelter ~ animal_type + intake_type + outcome_type + chip_status, family = quasipoisson(), data = data12)
summary(fitquasi)

```




## 6.Model comparison and parameter interpretation

To compare the Poisson-like distribution model with the Poisson distribution model, while making the original Poisson distribution model


```{r comparison for 2 models}
coef1 = coef(fitglm)
coef2 = coef(fitquasi)
se.coef1 = se.coef(fitglm)
se.coef2 = se.coef(fitquasi)
models.both <- cbind(coef1,se.coef1,coef2,se.coef2,exponent = exp(coef1))
models.both
```
Comparing the results of the above two model parameters shows that the parameter estimates are consistent while the standard errors are different.
In the case of over-discrepancy, the t-value/p-value of the Poisson-like results should be used to test the significance of the independent variables.



```{r}
pchisq(fitquasi$deviance,df = fitquasi$df.residual,lower.tail = FALSE)

```
Passes the chi-square test

(Explanation of model parameters)

## 7.Summary

(Response to questions, summary of results.)

## 8.Future work

1.The problem of too many zero values in the data, consider the zero-inflated Poisson distribution model.

```{r zero-inflation}

table(data12$time_at_shelter)
zeroani <- subset(data12$animal_type, data12$time_at_shelter == "0")
table(zeroani)

zeroani <- as.data.frame(zeroani)

pani <- ggpiestats(data12,'animal_type',
                   results.subtitle = F,
                   palette = 'Pastel2')
pani
pani2 <- ggpiestats(zeroani,'zeroani',
                   results.subtitle = F,
                   palette = 'Pastel2')
pani2


zeroint <- subset(data12$intake_type, data12$time_at_shelter == "0")
table(zeroint)
zeroint <- as.data.frame(zeroint)

table(data12$intake_type)

pint <- ggpiestats(data12,'intake_type',
                   results.subtitle = F,
                   palette = 'Pastel2')
pint

pint2 <- ggpiestats(zeroint,'zeroint',
                   results.subtitle = F,
                   palette = 'Pastel2')
pint2

zeroout <- subset(data12$outcome_type, data12$time_at_shelter == "0" )
zeroout <- as.data.frame(zeroout)
table(zeroout)
table(data12$outcome_type)

pout <- ggpiestats(data12,'outcome_type',
                   results.subtitle = F,
                   palette = 'Pastel2')
pout

pout2 <- ggpiestats(zeroout,'zeroout',
                   results.subtitle = F,
                   palette = 'Pastel2')
pout2


zerochip <- subset(data12$chip_status, data12$time_at_shelter == "0")
zerochip <- as.data.frame(zerochip)

table(data12$chip_status)

pchip <- ggpiestats(data12,'chip_status',
                   results.subtitle = F,
                   palette = 'Pastel2')
pchip

pchip2 <- ggpiestats(zerochip,'zerochip',
                    results.subtitle = F,
                    palette = 'Pastel2')
pchip2

ggarrange(pani,pani2,common.legend = T,legend = "left")
ggarrange(pint,pint2,common.legend = T,legend = "left")
ggarrange(pout,pout2,common.legend = T,legend = "left")
ggarrange(pchip,pchip2,common.legend = T,legend = "left")
```

It can be observed that the proportions of raw and zero-only screened values are almost similar for the remaining variables, except for the outcome variable, which has a significantly larger proportion of both types of euthanasia and return to owner. Given a realistic perspective, it is reasonable that these two types spend zero days in the shelter. Here we argue that the outcome variable can be classified as a zero-inflated intra-model variable, i.e. he is related to whether the number of days is >0, while the remaining three variables are point intra-model variables, i.e. they are related to the length of the days.

2.Multi-level zero-inflation problems: Most focus on 0 to 5, consider data grouping or a multi-level zero-inflation model.

## 9.Reference

Chen Qiang. Advanced econometrics and Stata applications [M]. Higher Education Press, 2014.

Xu Xin. (2020). A generalization of the zero-inflated generalized Poisson model and its application to actuarial calculations. Mathematical Statistics and Management

Wilson, P. 2015. The misuse of the Vuong test for non-nested models to test for zero-inflation. Economics Letters 127:51-53. -Link-, -PDF-

Van den Broek, J. (1995). A Score Test for Zero Inflation in a Poisson Distribution. Biometrics, 51(2), 738-743. -Link-, -PDF-

Vuong, Q. H. (1989). Likelihood Ratio Tests for Model Selection and Non-Nested Hypotheses. Econometrica, 57(2), 307–333. -Link-, -PDF-


